%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based on https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom 
\usepackage{fontawesome5} % for using icons
\usepackage{graphicx} % For scaling

\definecolor{secondaryColor}{RGB}{0, 79, 144}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Custom
\newcommand{\linkIcon}{\scalebox{0.75}{ \faExternalLink*}}
\newcommand{\link}[1]{\href{#1}{\linkIcon}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Mohamed Khalifa} \\ \vspace{1pt}
    \textbf{Software Engineer} \\  \vspace{3pt}
    % Software Engineer I
    \faMapMarker* Alexandria, Egypt $|$
    \href{tel:201029973998}{{\small {\footnotesize \faPhone*}\hspace*{0.13cm}20 102 997 3998}} $|$ 
    \href{mailto:makhalifa02@gmail.com}{\faEnvelope[regular]\hspace*{0.13cm}makhalifa02@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/5alifa}{\faLinkedinIn \hspace*{0.13cm}5alifa} $|$
    \href{https://github.com/5alifaa}{\faGithub\hspace*{0.13cm}5alifaa}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\item \small
Backend Software Engineer with experience building integrations, modernizing legacy systems, and shipping production features across commerce, ERP, healthcare, and AI-enabled products. Strongest in TypeScript/Node.js, Laravel, Go, PostgreSQL, and Odoo integrations, with hands-on experience in performance optimization, asynchronous systems, and business-critical workflows.
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{June 2025 –– Present}
      {\textbf{Cartona} \href{https://cartona.com/}{\linkIcon}}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Contributed to migrating the retailer backend from Rails to Laravel and Go, reducing API latency from 500ms–3s to around 90ms using OpenSearch and PostgreSQL.}
        \resumeItem{Built an Odoo integration to sync orders, inventory, and deliveries in real time with merchants’ ERP systems.}
        \resumeItem{Separated the enterprise order flow from the marketplace flow, moving the lifecycle into Odoo to align business workflows across purchasing, sales, and fulfillment operations.}
        \resumeItem{Investigated and fixed a payment bug caused by a race condition in asynchronous jobs.}
        \resumeItem{Contributed to designing the integration and transaction flow architecture for an upcoming credit platform, covering partner integrations, authentication, session handling, and transaction lifecycle.}        
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{Jan 2025 –– Jun 2025}
      {\textbf{Tech Hive} $|$ AppAsap \href{https://www.linkedin.com/company/appasap/posts/?feedView=all}{\linkIcon}}{Alexandria, Egypt}
      \resumeItemListStart
        \resumeItem{Built a GPT-based code generation tool that produced project structure, routes, and boilerplate from natural language prompts.}
        \resumeItem{Reduced cost and improved generation speed by adding caching and batching API calls.}
        \resumeItem{Implemented an RBAC system with Zod schemas to improve permission validation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{Laboratory Information System} (Freelance) $|$ \emph{Odoo, ERP, Healthcare}}{}
          \resumeItemListStart
            \resumeItem{Built an Odoo-based laboratory information system covering test ordering, sample tracking, results and reporting.}
            \resumeItem{Deployed the system in 2 production laboratories: \href{https://mozmenlabs.com/}{Mozmen Labs}\linkIcon \ and \href{https://www.elfanarlabs.com/}{El Fanar Labs}\linkIcon.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Mentor.AI} (Freelance) $|$ \emph{Next.js, LiveKit, WebRTC, OpenAI, Deepgram}}{}
          \resumeItemListStart
                    \resumeItem{Built a B2B AI platform for sales training and candidate evaluation via simulated voice calls.}
                    \resumeItem{Used LiveKit/WebRTC for calls and OpenAI/Deepgram for transcription and call evaluation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{iSkala} (Freelance) $|$ \emph{Next.js, PostgreSQL, Stripe}}{ \href{https://enrich.iskala.ai/}{live\linkIcon}}
          \resumeItemListStart
            \resumeItem{Built the backend for a B2B lead enrichment platform with email, LinkedIn, and phone lookup.}
            \resumeItem{Added AI email generation and a Stripe-based credit system.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{DealBlaster.ai} (Freelance) $|$ \emph{Next.js, Gmail API, Stripe}}{ \href{https://dealblaster.ai/}{live\linkIcon}}
          \resumeItemListStart
            \resumeItem{Built an email outreach platform that generates personalized cold emails using GPT.}
            \resumeItem{Integrated Stripe and Gmail API, supporting workflows sending 100+ emails per day.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Alexandria University}{Sept. 2019 –– Jul. 2023}
      {B.Sc. in Computer Science}{Alexandria, Egypt}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS & ACHIEVEMENTS-----------
\section{Achievements}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ECPC Contestant} \href{https://icpc.global/ICPCID/M851N8IAV7X1}{\linkIcon} $|$ Egyptian Collegiate Programming Contest (ICPC)}{2022}
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks}{: TypeScript, Node.js, Nest.js, Go, Laravel, Odoo (Python), Next.js} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, OpenSearch, Redis} \\
     \textbf{Infrastructure \& Tools}{: Docker, AWS, GitHub Actions, Sentry, New Relic} \\
    }}
 \end{itemize}

\end{document}
